Choose a License

### 2025-01-26 choose_license.qmd
Fix REUSE note

For example, if you previously created the file `create_data_dictionary.R`, you can now add the following comment to the beginning of the file, replacing `<YEAR>` and `<NAME>` with the current year and your name -- of course, you can also choose a different license:

```{.r filename="create_data_dictionary.R"}
# SPDX-FileCopyrightText: <YEAR> <NAME>
#
# SPDX-License-Identifier: CC0-1.0
```

@@

```{.bash .code-overflow-wrap filename="Terminal"}
reuse annotate --copyright="<NAME>" --license="CC0-1.0" create_data_dictionary.R
```

@@

```{.bash .code-overflow-wrap filename="Terminal"}
reuse annotate --copyright="Josephine Zerna <josephine.zerna@tu-dresden.de>" --copyright="Christoph Scheffel <christoph_scheffel@tu-dresden.de>" --copyright="Florian Kohrt" --license="CC-BY-4.0" --style=html Manuscript.qmd
```

@@

```{.html filename="Manuscript.qmd"}
<!--
SPDX-FileCopyrightText: 2024 Christoph Scheffel <christoph_scheffel@tu-dresden.de>
SPDX-FileCopyrightText: 2024 Florian Kohrt
SPDX-FileCopyrightText: 2024 Josephine Zerna <josephine.zerna@tu-dresden.de>

SPDX-License-Identifier: CC-BY-4.0
-->
```

Note that `Manuscript.qmd` was provided to you under [CC\ BY\ 4.0](https://creativecommons.org/licenses/by/4.0/), which is what you indicate with the previous comment. If you edited the file, you may also add yourself.^[For licenses that require that modifications are indicated, this is an easy way to comply with them, although you do not need to provide your real name.]

@@

```{.bash .code-overflow-wrap filename="Terminal"}
reuse annotate --copyright="Kristen Gorman" --license="CC0-1.0" data.csv
```

@@

```{.yml filename="data.csv.license"}
SPDX-FileCopyrightText: 2024 Kristen Gorman

>>>>

For example, if you previously created the file `create_data_dictionary.R`, you can now add the following comment to the beginning of the file, replacing `<YEAR>` and `<YOUR NAME>` with the current year and your name -- of course, you can also choose a different license:

```{.r filename="create_data_dictionary.R"}
# SPDX-FileCopyrightText: <YEAR> <YOUR NAME>
#
# SPDX-License-Identifier: CC0-1.0
```

@@

```{.bash .code-overflow-wrap filename="Terminal"}
reuse annotate --copyright="<YOUR NAME>" --license="CC0-1.0" create_data_dictionary.R
```

@@

```{.bash .code-overflow-wrap filename="Terminal"}
reuse annotate --copyright="Josephine Zerna" --copyright="Christoph Scheffel" --license="CC0-1.0" --style=html Manuscript.qmd
```

@@

```{.html filename="Manuscript.qmd"}
<!--
SPDX-FileCopyrightText: 2024 Christoph Scheffel
SPDX-FileCopyrightText: 2024 Josephine Zerna

SPDX-License-Identifier: CC0-1.0
-->
```

Note that `Manuscript.qmd` was provided to you under [CC0\ 1.0](https://creativecommons.org/publicdomain/zero/1.0/), which is what you indicate with the previous comment. As you edited the file throughout this tutorial, you may also add yourself.^[For licenses that require that modifications are indicated, this is an easy way to comply with them. Also, you do not need to provide your real name.]

@@

```{.bash .code-overflow-wrap filename="Terminal"}
reuse annotate --copyright="Allison Horst" --copyright="Alison Hill" --copyright="Kristen Gorman" --license="CC0-1.0" data.csv
```

@@

```{.yml filename="data.csv.license"}
SPDX-FileCopyrightText: 2024 Allison Horst
SPDX-FileCopyrightText: 2024 Alison Hill
SPDX-FileCopyrightText: 2024 Kristen Gorman
